% now in RST, don't edit this.

\subsection{File\_AT}


\subsubsection{Description}


File\_AT creates a File\_BDP that contains a reference to an arbitrary file. 
It has no real use (yet), except for bootstrapping a Flow\_AT series, 
where it can be used to test the (large scale) system performance.
See also Ingest\_AT for a real task that bootstraps a flow.

\subsubsection{Use Case}


Currently only used by Flow\_AT for testing purposes, and thus useful
to bootstap a flow, since it can start from an empty directory, and
create a zero length file.  This means you can create realistic flows,
in the same sense as full science flows, and measure the overhead
of ADMIT and the FlowManager.

\subsubsection{Input BDPs}

There are no input BDPs for this bootstrap AT. A filename is required to
create an output BDP, using an input keyword (see below).

\subsubsection{Input Keywords:}

\begin{description}

\item[file] The filename of the object. File does not have to exist yet.
  There is no default.

\item[touch]  Update timestamp (or create zero length file 
  if file did not exist yet)? Default: False.

\end{description}

\subsubsection{Output BDPs:}

\begin{description}

\item[File\_BDP] containing the string pointing to the file, following
  the same convention the other file containers (Image\_BDP,
  Table\_BDP) do, except their overhead.  There is no formal
  requirement this should be a relative or absolute address.  A
  symlink is allowed where the OS allows this, a zero length file is
  also allowed.

\end{description}

\subsubsection{Procedure}

Simple Unix tools, such as {\bf touch}, are used. No file existence test done.
There are no CASA dependencies, and thus no CASA tasks used.

% \subsubsection{CASA tasks used}
% none


\clearpage
