\subsection{LineList Design}

\subsubsection{Description}
An table of spectral lines detected in a spectrum, map, or cube.
Lines detected are an outcome of the procedure to take something
like a CubeSpectrum, CubeStats or PVCorr, with a known or unknown VLSR.
Cubes normally are references by frequency, but if already by velocity,
procedures are needed to find/identity aliases lines in the same band.

\subsubsection{Use Case}

\subsubsection{Inputs}
{\bf BDPs}\\
This AT will take one of the following input BDP's:
\begin{description}
\item[CubeSpectrum] with or without a CubeStats, if no CubseStats is supplied then a basic rms is computed from the input spectrum
\item[CubeStats] Peak/RMS
\item[PVSlice]
\item[SpectralMap]
\end{description}

{\bf Parameters}\\
\begin{description}
\item[]
\end{description}

\subsubsection{Products (LineList\_BDP)}
The AT will produce a single LineList\_BDP (with the exception of a SpectralMap as input, in this case a LineList\_BDP for each spectrum will be created). The items of the BDP will be a table with the following columns:
\begin{description}
\item[frequency] in GHz, precise to 5 digits
\item[unique identifier] ANAME-FFF.FFF ; e.g.  CO-115.27,   N2HP-93.173,   U-98.76
\item[likelihood] a number scaled 0...1 of detection probability, with 1 being most probable
\item[full name] CO, CO\_v1, C2H, H13CO+
\item[transition] Quantum numbers
\item[velocity] v$_{lsr}$ or offset velocity (based on rest frequency)
\item[energies] lower and upper state energies in K
\item[line strength] spectral line strength in D$^2$
\item[peak] the peak intensity of the line in Jy/bm
\item[fwhm] the FWHM of the line in km/s
\end{description}
Additionally an item to denote whether the velocity is v$_{lsr}$ or offset velocity. The offset velocity will only be used when the v$_{lsr}$ is not known and cannot be determined. The coordinates of where the line list applies along with units will also be stored.

\subsubsection{Line List Database}
The line list database will be the splatalogue subset that is already included with the CASA distribution.
\subsubsection{Proceedure}
\clearpage
